Report: Exploring Non-Parametric Entropy Estimators and Bootstrap Enhancements

### 2023-12-19 Code/R/RMarkdown/report2_plots_means.Rmd

```{r Plot_mean1, echo=FALSE, message=FALSE, warning=FALSE, out.width="100%", fig.show="hold", fig.align="center",  fig.cap="Mean entropy for Gamma SAR $L= 1$ and $\\mu=1$.", fig.width=6,fig.height=5}
set.seed(1234567890, kind = "Mersenne-Twister")

@@

>>>>

```{r SimulateDataPlot1, echo=FALSE, message=FALSE, warning=FALSE, out.width="100%", fig.show="hold", fig.align="center",  fig.cap="Mean entropy for Gamma SAR $L= 1$ and $\\mu=1$.", fig.width=6,fig.height=5}
set.seed(1234567890, kind = "Mersenne-Twister")

@@

entropy_data <-calculate_entropy(sample_sizes, R, mu, L)
```

```{r Plot1, echo=FALSE}
ggplot(entropy_data, aes(x = SampleSize, y = MeanEntropy, color = Estimator)) +
geom_point(size = 2) +
  geom_line(aes(group = Estimator), linetype = "solid", linewidth = 0.5) +
  geom_line(aes(y = true_entropy), linetype = "solid", color = "black") + 
  labs(title = "",
       x = "Sample Size", y = "Mean Entropy") +
       annotate("text", x = Inf, y = Inf, label = parse(text = sprintf("mu == %s", mu)), hjust = 1.08, vjust = 1.3, size = 3)
